### 2024-06-24 basic-statistics.qmd
20240623 - regression best-fit line

>>>>

```{r}
#| include: false
#| eval: false

set.seed(52242)
regression <- data.frame(outcome = rnorm(40, mean = 5, sd = 2))

regression$predictor <- complement(regression$outcome, .5)
regression$predictor <- regression$predictor + abs(min(regression$predictor))

lm(
  outcome ~ predictor,
  data = regression)

ggplot2::ggplot(
  data = regression,
  ggplot2::aes(
    x = predictor,
    y = outcome,
  )
) +
  ggplot2::geom_point() +
  ggplot2::geom_smooth(
    method = "lm",
    linewidth = 2,
    se = FALSE,
    fullrange = TRUE) +
  ggplot2::scale_x_continuous(
    lim = c(0,8),
    breaks = seq(from = 0, to = 8, by = 2),
    expand = c(0,0)
  ) +
  ggplot2::scale_y_continuous(
    lim = c(0,8),
    breaks = seq(from = 0, to = 8, by = 2),
    expand = c(0,0)
  ) +
  ggplot2::labs(
    x = "Predictor Variable",
    y = "Outcome Variable",
    title = "Regression Best-Fit Line"
  ) +
  ggplot2::theme_classic(
    base_size = 16) +
  ggplot2::theme(legend.title = element_blank())

ggsave("./images/regression.pdf", width = 6, height = 6)
```

A regression line is depicted in @fig-regression.

::: {#fig-regression}
![](images/regression.png)

A Regression Best-Fit Line.
:::
